### 2018-01-30 submission/manuscript.Rmd
update figure3 in manuscirpt

***Minimal Bray-Curtis Differences are Detected by Cycle Number:***
Overall, there was very little difference between each respective 5-cycle increment (e.g. 15x vs 20x) for both fecal and mock samples and this was consistent across the different sub-samplings used [Figure 3]. There were only two differences between 5-cycle increments that were identified. First, there were differences for the same fecal sample between 20x vs. 25x that was independent of HiFi DNA polymerase but dependent on sub-sampling depth (subsampled to 1000 = `r round(median(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`) (median (25% - 75% quantile)), subsampled to 5000 = `r round(median(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`), subsampled to 10000 = `r round(median(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3A-B]. Second, for the mocks, where data is available, there were larger difference between 20x and 25x (subsampled to 1000 = `r round(median(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3D]. However, these differences between the next 5 cycle increment do not persist once 25 cylces are reached [Figure 3].

@@

**Figure 3: Five Cycle Interval Community Differences.** A) Fecal samples sub-sampled to 1000 reads. B) Fecal samples sub-sampled to 5000 reads. C) Fecal samples sub-sampled to 10000 reads. D) Mock samples sub-sampled to 1000 reads. E) Mock samples sub-sampled to 5000 reads. F) Mock samples sub-sampled to 10000 reads. The solid black lines represent the median Bray-Curtis index difference within sample for each 5 cycle interval.

>>>>

***Minimal Bray-Curtis Differences are Detected by Cycle Number:***
Overall, there was very little difference between each respective 5-cycle increment (e.g. 15x vs 20x) for both fecal and mock samples and this was consistent across the different sub-samplings used [Figure 3]. There were only two differences between 5-cycle increments that were identified. First, there were differences for the same fecal sample between 20x vs. 25x that was independent of HiFi DNA polymerase but dependent on sub-sampling depth (subsampled to 1000 = `r round(median(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`) (median (25% - 75% quantile)), subsampled to 5000 = `r round(median(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`), subsampled to 10000 = `r round(median(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3A]. Second, for the mocks, where data is available, there were larger difference between 20x and 25x (subsampled to 1000 = `r round(median(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3B]. However, these differences between the next 5 cycle increment do not persist once 25 cylces are reached [Figure 3].

@@

**Figure 3: Community Differences by Five-Cycle Intervals and Sub-sampling Depth.** A) Fecal samples within person difference based on the next 5-cycle PCR interval. B) Mock samples within replicate difference based on the next 5-cycle PCR interval.

### 2018-01-30 submission/manuscript.tex
update figure3 in manuscirpt

\textbf{\emph{Minimal Bray-Curtis Differences are Detected by Cycle
Number:}} Overall, there was very little difference between each
respective 5-cycle increment (e.g.~15x vs 20x) for both fecal and mock
samples and this was consistent across the different sub-samplings used
{[}Figure 3{]}. There were only two differences between 5-cycle
increments that were identified. First, there were differences for the
same fecal sample between 20x vs.~25x that was independent of HiFi DNA
polymerase but dependent on sub-sampling depth (subsampled to 1000 =
0.51 (0.4 - 0.79) (median (25\% - 75\% quantile)), subsampled to 5000 =
0.43 (0.33 - 0.63), subsampled to 10000 = 0.4 (0.24 - 0.43)) {[}Figure
3A-B{]}. Second, for the mocks, where data is available, there were
larger difference between 20x and 25x (subsampled to 1000 = 0.88 (0.42 -
0.91)) {[}Figure 3D{]}. However, these differences between the next 5
cycle increment do not persist once 25 cylces are reached {[}Figure
3{]}.

@@

\textbf{Figure 3: Five Cycle Interval Community Differences.} A) Fecal
samples sub-sampled to 1000 reads. B) Fecal samples sub-sampled to 5000
reads. C) Fecal samples sub-sampled to 10000 reads. D) Mock samples
sub-sampled to 1000 reads. E) Mock samples sub-sampled to 5000 reads. F)
Mock samples sub-sampled to 10000 reads. The solid black lines represent
the median Bray-Curtis index difference within sample for each 5 cycle
interval.

>>>>

\textbf{\emph{Minimal Bray-Curtis Differences are Detected by Cycle
Number:}} Overall, there was very little difference between each
respective 5-cycle increment (e.g.~15x vs 20x) for both fecal and mock
samples and this was consistent across the different sub-samplings used
{[}Figure 3{]}. There were only two differences between 5-cycle
increments that were identified. First, there were differences for the
same fecal sample between 20x vs.~25x that was independent of HiFi DNA
polymerase but dependent on sub-sampling depth (subsampled to 1000 =
0.51 (0.4 - 0.79) (median (25\% - 75\% quantile)), subsampled to 5000 =
0.43 (0.33 - 0.63), subsampled to 10000 = 0.4 (0.24 - 0.43)) {[}Figure
3A{]}. Second, for the mocks, where data is available, there were larger
difference between 20x and 25x (subsampled to 1000 = 0.88 (0.42 - 0.91))
{[}Figure 3B{]}. However, these differences between the next 5 cycle
increment do not persist once 25 cylces are reached {[}Figure 3{]}.

@@

\textbf{Figure 3: Community Differences by Five-Cycle Intervals and
Sub-sampling Depth.} A) Fecal samples within person difference based on
the next 5-cycle PCR interval. B) Mock samples within replicate
difference based on the next 5-cycle PCR interval.
